### 2017-05-15 sheets/basis-2/sheet-basis-2.tex
Add answer environment for testing
Solved odd exercises by Felix.

@@

@@

@@

@@

>>>>

\begin{answer}
  Since $A\cong A'$ there are $f\in\mathscr A(A,A')$ and $g\in\mathscr A(A',A)$ such that $g \of f=1_A$ and $f \of g=1_A'$. Hence, $F(g)\of F(f)=F(g\of f)=F(1_A)=1_{F(A)}$ and $F(f)\of F(g)=F(f\of g)=F(1_A')=1_{F(A')}$. As a consequence, $F(f)$ is an isomorphism between $F(A)$ and $F(A')$. In particular, $F(A)\cong F(A')$.
\end{answer}

@@

\begin{answer}
  Suppose the discrete categories $\A$ and $\B$ with two and one objects respectively. Then, any functor $F\from A\to B$ is trivially faithful but $F(1_A)=F(1_B)$ (where $A$ and $B$ are the only objects of $\A$).
\end{answer}

@@

\begin{answer}
  \begin{enumerate}
  \item A subcategory of an ordered set $(S,\leq)$ is an ordered set $(S',\leq')$ such that $S'\subseteq S$ and $\leq'\;\subseteq\;\leq$.
  \item The subcategories of a group are either the category with no objects or submonoids of the group (which is of course a monoid). The only full subcategories are the group itself and the category with no objects. 
  \end{enumerate}
\end{answer}

@@

\begin{answer}
  Define
  \begin{align*}
    i(a)&=a &(a\in A)
  \end{align*}
  and
  \begin{align*}
    f(\epsilon)&=0_M&\\
    f(a_1\cdots a_{n-1}a_n)&=f(a_1\cdots a_{n-1})\of j(a_n) &\text{for }n>0.
  \end{align*}
  Clearly, for each $a\in A$, $f(i(a))=j(a)$, thus $f\of i=j$, and $f$ is a group homomorphism.

  Now, suppose $g$ is a group homomorphism satisfying $g\of i=j$. 
  Let $a_1\cdots a_n\in A^*$. Proof by induction on $n$ that $g(n)=f(n)$.

  Base case: $g(\epsilon)=0_M$ because $\epsilon$ is the neutral element in $A^*$).

  Inductive step: 
  \begin{align*}
    g(a_1\cdots a_{n-1}a_n)&=g(a_1\cdots a_{n-1})\of g(a_n)&g\text{ group homomorphism}\\
                           &=f(a_1\cdots a_{n-1})\of g(a_n)&\text{inductive hypothesis}\\
                           &=f(a_1\cdots a_{n-1})\of g(i(a_n)) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1})\of f(i(a_n)) & g\of i=j=f\of i\\
                           &=f(a_1\cdots a_{n-1})\of f(a_n) & a_n\in A\\
                           &=f(a_1\cdots a_{n-1}a_n)&f\text{ group homomorphism}
  \end{align*}
  Hence, $f=g$, so $f$ is indeed unique.

\end{answer}

@@

\begin{answer}
  \begin{enumerate}
  \item Consider $\A$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        E\arrow[r,yshift=.85ex,"s"] \arrow[r,below,yshift=-.85ex,"e"]&V
      \end{tikzcd}
    \]
    Then a functor $F\from \A\to\Set$ assigns to both $E$ and $V$ sets $E'$ and $V'$ (which correspond to the set of edges and vertices respectively) and to $s,e$ functions $s'$ and $e'$ that take edges $d$ from $E'$ and return elements $s'(d)$ and $e'(d)$ which correspond to the start and end node of the edge $d$ respectively.
  \item Consider $\B$ given by
    \[
      \begin{tikzcd}[column sep=huge,row sep=huge]
        A\arrow[r,yshift=.85ex,"f"] & B\arrow[l,below,yshift=-.85ex,"g"]
      \end{tikzcd}
    \]
    such that $g\of f=1_A$ and $f\of g=1_B$.
  \end{enumerate}
\end{answer}
